### 2024-09-03 README.Rmd
update Readme

This repository contains the documentation, results, and code of a project where we produce simple macroeconomic forecast distributions for the G7 economies, in the form of prediction intervals. It also contains code to continue to produce these forecasts in real-time. See the documentation below for further details.

@@

We generate easy-to-understand forecast intervals for output growth and inflation in the G7 economies, using the point forecasts published in the International Monetary Fund World Economic Outlook (IMF WEO). The forecast intervals are generated at the 50% and 80% levels in a simple and transparent manner, using empirical quantiles of the past history of point forecast errors in the IMF WEO. For more details, please refer to the working paper below.

@@

More details on each folder can be found further below.

Folder | Purpose
---|---
[`benchmarks`](benchmarks/) | Code and forecast data of benchmark forecasts.
[`data`](data/) | Processed WEO and benchmark forecast data. from `data-raw` ready to be used in the paper analysis.
[`miscellanous`](miscellanous/) | Files that are not relevant for the final analysis (exploratory scripts, presentation files, etc). Kept for transparency.
[`oecd_data`](oecd_data/) | OECD truth data used for fitting benchmarks and for robustness checks.
[`quantile_forecasts`](quantile_forecasts/) | The generated forecast intervals, recorded via their upper and lower endpoints. 
[`R`](R/) | R functions used in the analysis and for evaluation.
[`scores`](scores/) | Scores of forecasts.
[`scripts`](scripts/) | Executive scripts to produce all results.
[`specs`](specs/) | Specifications and global options for the analysis.

Forecast intervals at the 50% and 80% are recorded via their upper and lower endpoints, that is, the 0.25 and 0.75 predictive quantiles for the 50% interval, and the 0.1 and 0.9 predictive quantiles for the 90% interval.

The folders of this repository contain the following:

@@

- `benchmarks`: benchmark forecasts and the scripts that generate them.

@@

- `data`: WEO and merged data

@@

- `manuscript`: files to write manuscript. Abandoned now, in favor of `uqimf-manuscript` repository

@@

- `plots`: you get what you bargain for

- `presentation`: some files for the presentation of the project at the MathSEE Symposium

- `quantile-forecasts`: contains quantile forecasts as produced by `scripts/make-forecasts`, see below

- `scores`: Contains scores of forecasts in `quantile-forecasts` and BVAR benchmarks, at various levels of resolutions. Contains its own Readme file to explain what scores the different files contain.

- `scripts`: Contains scripts that process data based on the function in `R`

  - `toy-scripts`: small scripts to explore data

  - `plot-scripts`: scripts to generate plots

@@

  - `make-forecasts.R`: generate quantile forecasts based (`data/point-forecasts.csv` to `quantile_forecasts/quantile_forecasts.csv`)

@@

  - `score-forecasts.R`: score quantile forecasts, those generated here and the benchmark BVAR quantile forecasts.

>>>>

This repository contains the documentation, results, and code of a project where we produce simple macroeconomic forecast distributions for the G7 economies. It also contains code to continue to produce these forecasts in real-time. See the documentation below for further details.

@@

We generate easy-to-understand forecast intervals for output growth and inflation in the G7 economies, using the point forecasts published in the International Monetary Fund World Economic Outlook (IMF WEO). Our forecast intervals are generated at the 50% and 80% levels in a simple and transparent manner, using empirical quantiles of the past history of point forecast errors in the IMF WEO. For more details, please refer to the working paper below.

@@

More details on each folder can be found in its own respective section further below.

Folder | Purpose
---|---
[`benchmarks`](benchmarks/) | Code and forecast data of benchmark forecasts.
[`data`](data/) | Processed WEO and benchmark forecast data. 
[`miscellanous`](miscellanous/) | Files that are not relevant for the final analysis (exploratory scripts, presentation files, etc). Kept for completeness and transparency.
[`oecd_data`](oecd_data/) | OECD truth data used for fitting benchmarks and for robustness checks.
[`quantile_forecasts`](quantile_forecasts/) | The generated forecast intervals, recorded via their upper and lower endpoints. 
[`R`](R/) | R functions used in the analysis and for evaluation.
[`scores`](scores/) | Scores of forecasts. 
[`scripts`](scripts/) | Executive scripts to produce all results.
[`specs`](specs/) | Specifications and global options for the analysis.

## General notes on naming data files

Note that data files in this repository are generally identified with some "core-name", e.g. quantile_forecasts, and then with prefixes and/or suffixes that further describe deviations from the default setting.

- Default setting: training data (target years 2001-2012); absolute error method; IMF WEO truth data; complete data before discarding instances for scoring
- "ho" suffix: holdout data (target years 2013-2023)
- "directional" suffix: directional error method
- "oecd" prefix: OECD truth data (used for robustness check)
- "to_score" prefix: excludes some instances for scoring data. All scores in scores/ folder are calculated based on these data versions.

### R folder

@@

### benchmarks folder

@@

### data folder

@@

### oecd_data folder

@@

### quantile_forecasts folder

- `quantile-forecasts`: contains forecasts as produced by `scripts/make-forecasts`, see below. Note that the forecast intervals are identified via their upper and lower endpoints. That is, for the 50% interval, the 0.25 and 0.75 predictive quantiles, and for the 80% interval, the 0.1 and 0.9 predictive quantiles. Also note the naming data notes outlined above.

### scores folder

- `scores`: Contains scores of forecasts in `quantile-forecasts` and BVAR benchmarks, at various levels of resolutions. Contains its own Readme file to explain what scores the different files contain. Also note the naming data notes outlined above.

### scripts

- `scripts`: Contains scripts that process data based on the functions in `R`
  - `master.R`: produces all results based on the following sub-scripts (listed in the order as they appear in master.R, so not alphabetical)

@@

@@

  - `encode-missing-predictions.R` explicitly encode missing data (although we actually have no missing data, but just for completenss)

  - `make-forecasts.R`: generate forecast intervals

  - `exclude-from-scoring.R`: exclude any instances that are listed in `specs/specs.R` from scoring

  - `score-forecasts.R`: score quantile forecasts, those generated in `make-forecasts.R` and the benchmark BVAR quantile forecasts.
